ABC inferences

### 2024-12-16 extensive_tests/abc_inferences/draft-abc-inferences-vignette.Rmd
Updating script get_spatial_str of abc_inferences workflow

---
title: "ABC inferences"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ABC Inferences with MethEvolSIM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

@@

Add info on how to download the reference genome from progress report.

-Requires: CGI annotation file (.txt file obtained with makeCGI) **Add reference**

@@

X-axis corresponds to the positions in chromosome `r dpp4_chr`
dpp4_start
dpp4_end

@@

If using this region the number of CpG sites to simulate would be:

@@

with number of non-island (0) and island (1) structures:

@@

>>>>

---
title: "ABC inferences"
output: 
  rmarkdown::html_vignette:
    toc: true
bibliography: references.bib
vignette: >
  %\VignetteIndexEntry{ABC Inferences with MethEvolSIM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,  # Set the figure width to match the text width
  fig.height = 5, # Set the figure height
  out.width = "100%"  # Ensure it takes up 100% of the available width in HTML
)
```

@@

-Requires: CGI annotation file (`.txt` file) obtained with makeCGI v1.3.4 [@hiddenMarkov]

- The genome assembly file: Obtain the FASTA file ([GCF_000238955.4_M_zebra_UMD2a_genomic.fa](https://www.ncbi.nlm.nih.gov/datasets/genome/GCF_000238955.4/)) from NCBI (file source *RefSeq*, file type *Genome Sequences (FASTA)*)

@@

Genomic region close to gene *dpp4*. X-axis corresponds to the positions in chromosome `r dpp4_chr`. Y-axis corresponds to CpG counts at each genomic region. Each genomic region is represented by a bar starting and ending in the corresponding chromosome position. Vertical black lines represent start and end of gene *dpp4*.

@@

Genomic region close to gene *dpp4*. X-axis corresponds to the positions in chromosome `r dpp4_chr`. Y-axis corresponds to CpG density at each genomic region. Each genomic region is represented by a dot at its corresponding genome start position. Vertical black lines represent start and end of gene *dpp4*.

When using this region the number of CpG sites to simulate would be:

@@

with number of non-island and island structures:

@@

# References
